\documentclass[10pt]{article}
\usepackage{array, xcolor, lipsum, bibentry}
\usepackage[margin=3cm]{geometry}
\usepackage[colorlinks=true, linkcolor=darkblue, urlcolor=darkblue, citecolor=darkblue]{hyperref} 
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{longtable}

\title{\bfseries Eugene Usenko}
\author{zhenya.usenko@gmail.com}
\date{}
 
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.2pt}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.7}
 
\begin{document}
\maketitle
% \vspace{1em}
% \begin{minipage}[ht]{0.48\textwidth}
% Main Road 25\\
% City 12345\\
% State of Sabotage
% \end{minipage}
% \begin{minipage}[ht]{0.48\textwidth}
% Nonlandian\\
% January 3rd, 2020\\
% +12 34 56 789
% \end{minipage}
% \vspace{20pt}
 
\section*{Objective}
As a seasoned Full Stack Developer and Technical Lead, I bring over 20 years of experience in designing and implementing robust software solutions across various industries and domains. My expertise spans frontend, backend and mobile development, architecture redesign, CI/CD implementation using cutting-edge technologies like NodeJS, TypeScript, ReactJS, Java, Docker/Kubernetes. I am passionate about leading teams to deliver high-quality products, optimizing existing systems, and driving innovation through scalable and maintainable code. Seeking to leverage my skills and experience in a challenging role that allows me to contribute to impactful projects and guide teams toward success.
 
\section*{Professional Experience}
\begin{tabular}{L!{\VRule}R}
2015--today&{\bf Teamlead and Software Architect at \href{https://www.luxoft.com/}{Luxoft}.}\\
&Head of FE development team. Redesigned architecture from monolith to granular. Introduced an API for the 3-d parties for smooth integration of apps into a main solution. Migrated FE development stack from Java/GWT to ReactJS/Redux. Built development processes like automation/code review/e2e and incorporated deployment pipelines using Docker/Kubernets. Tightly worked with the customer on prototyping, feature validation and UX improvements.\\

\noalign{\vskip 0.5cm}
2014--215&{\bf TechLead at \href{https://www.playtika.com/}{Playtika}.}\\
&Led the refactoring team in implementing a new data layer for a high-traffic backend (~100k daily active users). Coordinated development efforts across feature teams.\\

\noalign{\vskip 0.5cm}
2010--2014&{\bf Sr. Software Engineer, TechLead at \href{https://www.softserveinc.com/}{SoftServe}.}\\&Contributed to various projects in multiple roles, including desktop, back-end, and mobile software engineer, as well as Tech Lead. Led feature implementation, architectural design and redesign, team coaching, and maintained effective communication with clients.\\

\noalign{\vskip 0.5cm}
2008--2010&{\bf Sr. Software Engineer at \href{https://isd.dp.ua/}{ISD}.}\\&Was responsible for server-side logic and services development. Designed an API contract for 3-d party systems integration. Contributed to relocating a project to our location, prepared the migration plan, and facilitated knowledge sharing for local teams.\\

\noalign{\vskip 0.5cm}
2005--2008&{\bf Sr. Software Engineer at \href{https://www.rts.ua/}{RTS-Ukraine}.}\\&Primarily focused on UI implementation using Java frameworks. Additionally gained experience in low-level, client/server programming, developing drivers, and reverse engineering.\\
\end{tabular}
 
\section*{Education \& Certificates}
\begin{tabular}{L!{\VRule}R}
2017&\href{https://university.mongodb.com/course_completion/1ad65bdb-de01-42b0-8fa8-5de09f83}{M101JS: MongoDB for Node.js Developers}\\
2012&Java OCJP 1.6(1Z0-851)\\
2001--2006&{Master of Automation of Technological Processes, \href{http://pgasa.dp.ua/en/}{PSACEA}, Ukraine.}\\%[5pt]
\end{tabular}
 
\section*{Additional Information}
\begin{tabular}{L!{\VRule}R}
Languages& Ukrainian, Russian, \bf{English B2} \\
\end{tabular}
 
\bibliographystyle{plain}
\nobibliography{publication}
 
\section*{Projects}
\begin{longtable}{L!{\VRule}R}

\noalign{\vskip 0.5cm}
2024--now&{\bf {Drone detector}}. \\&
Personal R\&D project focused on detecting and classifying UAVs. The project incorporates technologies such as Software-Defined Radio (SDR), Digital Signal Processing (DSP), and Deep Learning for signal classification using raw IQ data. Several challenges were addressed, including the implementation of rapid scanning across a wide range of frequencies and prototyping and evaluating different deep learning models to ensure functionality on an embedded edge device.\\&
\texttt{C++, Python, TensorFlow, SDR/DSP} \\

\noalign{\vskip 0.5cm}
2015--2023&{\bf \href{https://dboard.lu/}{DBoard}}. \\&
Led the frontend team, gaining the customer's trust by proposing and successfully implementing a long-term refactoring plan. Evolved the entire application suite by migrating from a monolithic to a granular architecture, which increased application reliability. Planned and executed the migration of the development stack, significantly improving performance, which in turn allowed for product promotion and the attraction of more users. Worked closely on new feature proposals and validation. Implemented numerous improvements to development and testing processes, including the introduction of CI/CD and the establishment of feature teams.  \\&
\texttt{Java, GWT, Tomcat, JavaScript, HTML/CSS, TypeScript, React/Redux, NodeJS, Nginx, Docker/K8S, Figma/Sketch} \\

\noalign{\vskip 0.5cm}
2015--2018&{\bf \href{https://www.slideshare.net/slideshow/luxoft-horizon/43900137}{Horizon Platform}}. \\&
Managed a small team of developers responsible for maintaining a legacy UI platform for data analytics. \\&
\texttt{Java, Spring IoC/MVC, GWT, Tomcat, JavaScript, HTML/CSS} \\

\noalign{\vskip 0.5cm}
2014--2015&{\bf \href{https://caesarspalaceonline.com/}{Caesars Casino}}. \\&
Managed a refactoring team focused on improving the backend of a high-load application. Led and participated in the refactoring of the data layer, which resulted in enhanced API integration and overall performance, enabling faster feature implementations. Acted as a technical mediator between multiple feature teams to plan a delivery roadmap that avoided breaking changes.\\&
\texttt{Java, Spring IoC/MVC, MySQL, CouchBase} \\

\newpage
\noalign{\vskip 0.5cm}
2013--2014&{\bf \href{https://www.wunderground.com/}{Weather Underground}}. \\&
There was a request from the customer to analyze the mobile application architecture and provide a solution for redesigning the map engine. As a result, significant performance improvements through several changes were done, including splitting the app into separate components (UI and services) and implementing predictive map rendering.\\&
\texttt{Java, Android} \\

\noalign{\vskip 0.5cm}
2012--2013&{\bf \href{https://www.cnet.com/reviews/logitech-bemo-review/}{Bemo}}. \\&
Participated as the lead of the Android team in a pilot R\&D project. Designed the application architecture, UI, and several subsystems, including media file management, gallery synchronization, effects editor, video streaming, and a player for media files.\\&
\texttt{Java, Java JNI, C, Android} \\

\noalign{\vskip 0.5cm}
2011--2012&{\bf \href{https://alert.logitech.com/}{Alert}}. \\&
Redesigned the architecture of the Android client application. Implemented real-time video streaming, including an H264 video player with a decoder, for indoor and outdoor cameras. Optimized the existing MJPEG streaming and overall application architecture. Improved overall application performance and UX.\\&
\texttt{Java, Java JNI, C, Android} \\

\noalign{\vskip 0.5cm}
2011--2011&{\bf iText}. \\&
Developed an Android application for a custom Android board. Implemented log management and developed the integration and communication layer with ZigBee sensors.\\&
\texttt{Java, Java JNI, C, Android} \\

\noalign{\vskip 0.5cm}
2011--2011&{\bf Gazzang}. \\&
Implemented e2e test for the secure cloud storage.\\&
\texttt{Python} \\

\noalign{\vskip 0.5cm}
2011--2011&{\bf TestSurvey}. \\&
Developed a desktop application for managing and executing tests with complex branching logic.\\&
\texttt{Java, ANTLR} \\

\noalign{\vskip 0.5cm}
2010--2011&{\bf Basecamp}. \\&
Developed a web-based analytics application for the financial department.\\&
\texttt{Java, Spring IoT/MVC, HTML/CSS} \\

\noalign{\vskip 0.5cm}
2010--2010&{\bf Genetics}. \\&
Contributed to the development and refactoring of an application suite in the healthcare domain. Led the project relocation to a local office and coached a team of developers who were designated to maintain it in the future. \\&
\texttt{Java, JBoss, EJB3, Oracle database} \\

\newpage
\noalign{\vskip 0.5cm}
2008--2010&{\bf TotalQC}. \\&
Developed and refactored number of web services. Was responsible for integration with 3-d party applications. \\&
\texttt{Java, JBoss, EJB3, Oracle database} \\

\noalign{\vskip 0.5cm}
2005--2008&{\bf \href{https://rts-soft.com/en/products/s3/}{S3-IDE}.} \\&
Developed desktop applications and UI features using the NetBeans Platform. Implemented a code editor with syntax highlighting for the \texttt{PLC} programming language and created a client/server application for managing project files on remote embedded systems. \\&
\texttt{Java, Swing, NetBeans Platform, ANTLR, C} \\

\noalign{\vskip 0.5cm}
2005--2008&{\bf \href{https://rts-soft.com/en/products/octavo/}{Octavo}.} \\&
Developed desktop applications and UI features. Implemented various drivers for digital/analog I/O boards and modules for QNX RTOS. Reverse-engineered several Linux drivers.\\&
\texttt{Java, SWT, Swing, C, QNX}
\end{longtable}
 
\end{document}

% https://texblog.org/2012/04/25/writing-a-cv-in-latex/
https://latex-tutorial.com/cv-latex-guide/
